### 2019-03-04 report/final-report.tex
fig caption

\begin{figure}
  \centering
  \includegraphics{figs/examples.eps}
  \caption{Average number of random examples required to synthesize benchmark
    programs.  {\bf Experimental Average} is the average number of randomly
    generated examples needed to correctly synthesize the lens.  {\bf
      Determinize Permutations} is the theoretical number of examples required
    to determinize the choice all the permutations in \RigidSynth{}.
    In practice, far fewer examples are
    needed to synthesize the correct lens than would be predicted by the number
    required to determinize permutations.}
  \label{fig:exs-reqd}
\end{figure}

@@

\subsection{Simple Symmetric Lens Synthesis}
Finally, we implemented simple symmetric lenses as an extension to
Boomerang~\cite{boomerang}.  
This allows users
to write synthesis tasks 
alongside lens combinators, incorporate synthesis results into manually-written
lenses, and reference previously defined lenses during synthesis. All experiments
were performed on a 2.5 GHz Intel Core i7 processor with 16 GB of 1600 MHz DDR3
running macOS Mojave.

>>>>

\begin{figure}
  \centering
  \includegraphics{figs/examples.eps}
  \caption{Average number of random examples required to synthesize benchmark
    programs.  {\bf Examples Required} is the average number of randomly
    generated examples needed to correctly synthesize the lens.  {\bf
      Determinize Permutations} is the theoretical number of examples required
    to determinize the choice all the permutations in \RigidSynth{}.
    In practice, far fewer examples are
    needed to synthesize the correct lens than would be predicted by the number
    required to determinize permutations.}
  \label{fig:exs-reqd}
\end{figure}

@@

\subsection{Simple Symmetric Lens Synthesis}
In addition to the results above, we implemented simple symmetric lenses as an extension to
Boomerang~\cite{boomerang}.  
This allows users
to write synthesis tasks 
alongside lens combinators, incorporate synthesis results into manually-written
lenses, and reference previously defined lenses during synthesis. All experiments
were performed on a 2.5 GHz Intel Core i7 processor with 16 GB of 1600 MHz DDR3
running macOS Mojave.
